Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/paper.tex
added macros
Update paper.tex
added numbers to abstract

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{stmaryrd}
\usepackage{booktabs} % for professional tables
\usepackage{paralist}

@@

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
\newcommand{\mpv}[1]{\textcolor{green}{{\bf MV:} #1}}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

\begin{abstract}
As neural networks are being increasingly deployed in 
different applications and on different hardware, it has
become increasingly important to optimize inference time
and model size along with model accuracy.
Most current work optimizes model size, model accuracy and
inference time in different stages and results in suboptimal
results at the cost of computational inefficiency.
In this work, we propose a new techique called ShrinkNets that
optimizes all three of these metrics simultaneously by learning
optimal network size at training time.
Specifically our technique presents a new method to simultaneously optimize network size and model performance by neuron-level pruning.
Neuron-level pruning not only produces much smaller 
networks for a given accuracy threshold but also produces
dense weight matrices that are efficient at inference time.
By applying our technique to a variety of models with both convolutional and fully connected layers, we show that ShrinkNets can reduce XXX by YYY and ZZZ by AAA in only BBB amount of time.

\end{abstract}

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{stmaryrd}
\usepackage{booktabs} % for professional tables
\usepackage{paralist}
\usepackage{xspace}

@@

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
\newcommand{\mpv}[1]{\textcolor{green}{{\bf MV:} #1}}
\newcommand{\shrink}{{\bf ShrinkNets}\xspace}
\newcommand{\swl}{{\bf SwitchLayer}\xspace}
\newcommand{\swls}{{\bf SwitchLayers}\xspace}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

\begin{abstract}
As neural networks are being increasingly deployed in different applications and
on different hardware, it has become increasingly important to optimize
inference time and model size along with model accuracy.  Most current work
optimizes model size, model accuracy and inference time in different stages and
results in suboptimal results at the cost of computational inefficiency.  In
this work, we propose a new techique called ShrinkNets that optimizes all three
of these metrics simultaneously by learning optimal network size at training
time.  Specifically our technique presents a new method to simultaneously
optimize network size and model performance by neuron-level pruning.
Neuron-level pruning not only produces much smaller networks for a given
accuracy threshold but also produces dense weight matrices that are efficient at
inference time.  By applying our technique to a variety of models with both
convolutional and fully connected layers, we show that ShrinkNets can reduce by
35\% the network size with respect to a static network for \texttt{CIFAR10}, and
it can achieve speedups during inference time of up to 40X. In addition, the
most accurate networks found by ShrinkNets are similar or more accurate than
those found by statically trained networks.  
\end{abstract}
